---
title: "R Notebook"
output: html_notebook
---

This is an R notebook for  [United Nations General Assembly Voting Data](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/LEJUQZ). The dataset indicates the voting patterns of member countries of United Nations from 1946 to 2020. The data Code book can be downloaded here [source](https://dataverse.harvard.edu/api/access/datafile/:persistentId?persistentId=doi:10.7910/DVN/LEJUQZ/DYNZPA)


```{r}
# loading libraries 
library(readr)
library(visdat)
library(ggplot2)
library(dplyr)
```

```{r}
path = "C:/Users/adeso/Desktop/Training/Portfolio/Data/UNVotes.csv"
un_raw = read.csv(path)
head(un_raw)
```
```{r}
# Select columns important to the objective of the project
un_df = subset(un_raw, select = c(vote, Country, Countryname, year, session)) %>%
  mutate(session = session + 1945) %>%
  filter(vote <= 3)
head(un_df)
```
```{r}
glimpse(un_df)
```
```{r}
vis_dat(un_df, warn_large_data = FALSE)
```


```{r}
summ_by_year = un_df %>% group_by(year) %>%
  summarise(total = n(),
            percent_vote_Yes = mean(vote == 1),
            percent_Abstain = mean(vote == 2),
            percent_vote_No = mean(vote == 3))

```

```{r}
ggplot(summ_by_year, aes(year,  total)) +
  geom_point()
```

```{r}
ctry = c("Nigeria","Ghana","Egypt","Morocco","Ethiopia","Kenya","South Africa", "Namibia","Angola","Gabon", "United States of America", "France", "United Kingdom of Great Britain and Northern Ireland")

sum_country = un_df %>% group_by(Countryname, year) %>%
  filter(Countryname %in% ctry) %>%
  summarise(total = n(),
            percent_vote_Yes = mean(vote == 1),
            percent_ab = mean(vote == 2),
            percent_vote_No = mean(vote == 3)) %>%
  arrange(desc(percent_vote_Yes))
sum_country
```
```{r}
  ggplot(sum_country , aes(year, percent_vote_Yes, color=Countryname)) +
  geom_line() 
```
```{r}
ggplot(sum_country , aes(year, percent_vote_Yes)) +
  geom_line() + 
  facet_wrap(~Countryname, scales = "free_y")
```
```{r}
Nigeria_Ghana = sum_country %>% filter(Countryname %in% c("Nigeria", "Ghana"))
ggplot(Nigeria_Ghana , aes(year, percent_vote_Yes, color=Countryname)) +
  geom_line()
```
```{r}
Morocco_Egypt = sum_country %>% filter(Countryname %in% c("Morocco", "Egypt"))
ggplot(Morocco_Egypt , aes(year, percent_vote_Yes, color=Countryname)) +
  geom_line()
```
```{r}
Kenya_Ethiopia = sum_country %>% filter(Countryname %in% c("Kenya", "Ethiopia"))
ggplot(Kenya_Ethiopia , aes(year, percent_vote_Yes, color=Countryname)) +
  geom_line()
```
```{r}
South_Africa_Namibia = sum_country %>% filter(Countryname %in% c("South Africa", "Namibia"))
ggplot(South_Africa_Namibia , aes(year, percent_vote_Yes, color=Countryname)) +
  geom_line()
```
```{r}
Angola_Gabon = sum_country %>% filter(Countryname %in% c("Angola", "Gabon"))
ggplot(Angola_Gabon , aes(year, percent_vote_Yes, color=Countryname)) +
  geom_line()
```

```{r}
un_data = un_df %>% 
  mutate(vote = as.factor(vote),member = as.logical(member)) 

#vis_dat(un_df, warn_large_data = FALSE)
```

```{r}
head(un_data)
```
```{r}
countries <- c("USA", "UK",
               "CAN", "HTI", "CUB", "DOM")

un_data %>% 
  group_by(year, Countryname) %>%
  filter(Country %in% countries, year == 2000) %>%
  summarise(total = n(), percent_yes = mean(vote == 1))
```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.




